### 2021-04-22 assertions/doc/thesis-bernhardt/chapters/3-offline_design.tex
Begin revision chpt 5

\chapter{Toolchain Implementation - Frontend}\label{chap:offline}
The purpose of the toolchain is to support the process from specifying assertions to generating assertion Smart Contracts that can be invoked on-chain by the validators. As determined in \secref{sec:restrict}, the current version of the toolchain only supports the processing of assertions featuring universal quantification. The toolchain was developed in the programming language OCaml \cite{ocaml_docs} --- the code is available in a GitHub\footnote{\url{https://github.com/proglang/thesis-distributed-assertion-checking}\todo{commit}} repository of the Chair of Programming Languages.

>>>>

\chapter{Toolchain Frontend}\label{chap:offline}
The purpose of the toolchain is to support the process from specifying assertions to generating assertion Smart Contracts that can be invoked on-chain by the validators. As determined in \secref{sec:restrict}, the current version of the toolchain only supports the processing of assertions featuring universal quantification. The toolchain was developed in the programming language OCaml \cite{ocaml_docs} --- the code is available in a GitHub\footnote{\url{https://github.com/proglang/thesis-distributed-assertion-checking}\todo{commit}} repository of the Chair of Programming Languages.

### 2021-04-22 assertions/doc/thesis-bernhardt/chapters/5-offline_design_tezos.tex
Begin revision chpt 5

\todo{Make clear that we only engage validators on Tezos (not all nodes)}
\todo{What happens if a validator has multiple endorsing rights?}
\chapter{Tezos-specific Offline Design}\label{chap:offline_tezos}
After parsing an assertion contract and transforming it, the resulting AST is passed to the target-specific backend. For this thesis, the platform target is Tezos, with Michelson as the compilation target. This chapter continues to describe the pipeline stages implemented in the Tezos backend, which are shown in \figref{fig:pipeline_backend}. Furthermore, it states the necessary extensions to Michelson and its evaluator to facilitate useful assertions using random generators and assesses several orchestration strategies between the parent and assertion contract code. As a preliminary, the following section gives a short introduction to the Tezos blockchain, the Michelson language and some relevant tools in Tezos' ecosystem.

@@

\section{Backend of the pipeline}
The Tezos backend of the pipeline comprises of the three stages semantic check, type check and compilation. During the semantic check, the common AST is cast to a Tezos-specific AST type. If the assertion contains any data types or operations not supported in Michelson, the assertion contract is rejected. Since the subsequent stages are less straight forward, they are explained in more detail in the following.
\begin{figure}[h]
\includegraphics[width=\linewidth]{figures/5-offline_tezos/pipeline_backend}
\caption{The stages of Tezos-specific backend of the compilation pipeline}
\label{fig:pipeline_backend}
\end{figure}

@@

>>>>

\chapter{Toolchain Backend}\label{chap:offline_tezos}
After parsing and transforming a list of assertions, the resulting ASTs are passed to the target-specific backend. For this thesis, the platform target is Tezos, with Michelson as the compilation target. The pipeline stages of the backend comprise the ones colourized in \figref{fig:pipeline_backend}. First, the generic ASTs are subjected to a semantic check, which rejects any assertions containing unsupported types, operations or other invalid expressions. Valid ASTs are then cast to a target specific AST type and passed to the type checker. In this stage, the assertions are linked to the respective parent entrypoints based on the parameter patterns and tags. Given the list of target specific ASTs and a linking, the compiler finally generates target code. Each stage is described in more detail in \secref{sec:backend_impl}.

As a preliminary for the compiler implementation, 
% the chapter identifies/describes necessary amendments to Michelson and the VM -> part of protocol design, but also concerns the toolchain -> secref
% furthermore, a scheme for the orchestration of assertion and parent code is required. the code somehow needs to collude -> explores some options; discusses advantages and disadvantages. picks a winner for the proof-of-concept impl.
% for background/ as a basis for this chapter, section 1 gives an introduction to Tezos and Michelson

 Furthermore, it states the necessary extensions to Michelson and its evaluator to facilitate useful assertions using random generators and assesses several orchestration strategies between the parent and assertion contract code. As a preliminary, the following section gives a short introduction to the Tezos blockchain, the Michelson language and some relevant tools in Tezos' ecosystem.

@@

\section{Backend implementation}\label{sec:backend_impl}
\todo{Shorten a bit - overview already given in chpt intro}
The Tezos backend of the pipeline comprises of the three stages semantic check, type check and compilation. During the semantic check, the common AST is cast to a Tezos-specific AST type. If the assertion contains any data types or operations not supported in Michelson, the assertion contract is rejected. Since the subsequent stages are less straight forward, they are explained in more detail in the following.
\begin{figure}[h]
\includegraphics[width=\linewidth]{figures/5-offline_tezos/pipeline_backend}
\caption{The stages of Tezos-specific backend of the compilation pipeline}
\label{fig:pipeline_backend}
\end{figure}

@@

\todo{Make clear that we only engage validators on Tezos (not all nodes)}
\todo{What happens if a validator has multiple endorsing rights?}
